What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-11 Manuscript/MS- What is LDD.tex
Final edits to the Introduction.

An added difficulty to bridge ecological processes of dispersal with their genetic consequences is the fact that dispersal per se does not necessarily imply realized gene flow \citep{Mallet:2001wx}. Yet in the genetics literature, the inescapable difficulty to robustly estimate $\sigma_x$, the the standard deviation of parent-offspring distances, as an estimate of realized gene flow distance, is analogous to the ecological scenario. Strongly leptokurtic distributions of dispersal distances would lead to severe underestimation of $\sigma_x$, e.g., in mark-recapture studies limited to local sites where the long tail of LDD events escapes detection beyond the edges of the study area \citep{Mallet:2001wx}. Thus, fat-tailed distributions of dispersal distances tend to homogenize distant populations, leading to stronger reductions in $F_{st}$ than expected from local records of dispersal events \citep{Rousset:1997bd}.

@@

LDD events have two key characteristics that make them extremely important for population dynamics, yet being very difficult to characterize: LDD events are infrequent, but with a disproportionately high influence on contemporary gene flow and structure of the genetic pools \citep[e.g., ][]{Schurr2009long,Clobert:2012vw,Travis:2013en}. LDDs can connect disparate populations, allowing for genetic connectivity, colonization of vacant habitat and range expansion across changing landscapes, and maintain global persistence in the face of local extinctions \citep{Trakhtenbrot:2005ij,Baguette:2006aa,Ronce:2007hc,Schloss:2012gt}. With their influence on the structure of genetic pools, LDD events can also drive population differentiation and speciation \citep{Ronce:2007hc}.

>>>>

An added difficulty to bridge ecological processes of dispersal with their genetic consequences is the fact that dispersal per se does not necessarily imply realized gene flow \citep{Mallet:2001wx}. Yet in the genetics literature, the inescapable difficulty to robustly estimate $\sigma_x$, the the standard deviation of parent-offspring distances, as an estimate of realized gene flow distance, is analogous to the ecological scenario. Strongly leptokurtic distributions of dispersal distances would lead to severe underestimation of $\sigma_x$, e.g., in mark-recapture studies limited to local sites where the long tail of LDD events escapes detection beyond the edges of the study area \citep{Mallet:2001wx}. Thus, fat-tailed distributions of dispersal distances tend to homogenize distant populations, leading to stronger reductions in $F_{st}$ than expected from local records of dispersal events \citep{Rousset:1997bd}. Despite such difficulties, comparative approaches \citep[e.g.,][]{Bohonak:1999aa} demonstrate that dispersal makes a measurable contribution to population genetic differentiation in most animal species in nature, and that gene flow estimates are rarely so overwhelmed by population history, departures from equilibrium, or other microevolutionary forces as to be uninformative. The relationship between dispersal and realized gene flow is key to understand how migration interacts with drift in driving the dynamics of genetic pools and population differentiation \citep{Garant:2007cka}.

@@

LDD events have two key characteristics that make them extremely important for population dynamics, yet being very difficult to characterize: LDD events are infrequent, but with a disproportionately high influence on contemporary gene flow and structure of the genetic pools \citep[e.g., ][]{Schurr2009long,Clobert:2012vw,Travis:2013en}. LDDs can connect disparate populations, allowing for genetic connectivity, colonization of vacant habitat and range expansion across changing landscapes, and maintain global persistence in the face of local extinctions \citep{Trakhtenbrot:2005ij,Baguette:2006aa,Ronce:2007hc,Schloss:2012gt}. With their influence on the structure of genetic pools, LDD events can also drive population differentiation and speciation \citep{Garant:2007cka,Ronce:2007hc}.
